Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-29 main.tex
Update on Overleaf.

\section{Introduction}
% can I work "Currents of Space" into this paper somehow (Asimov)?
Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}). One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
%
% get a sentence with a better punch at the end
%

@@

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically
%mm [added Fragile+ 2004 because they studied distributed metal injection.]
\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004},
and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}. The simulation discussed here was introduced in detail in
%mm don't forget to introduce into bibliography
Emerick et al.\ (2018; hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

>>>>

\section{Introduction}
Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}). One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
%
% get a sentence with a better punch at the end
%

@@

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}. The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
